### 2014-09-22 Paper1/paper1.tex
Overwrite this

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
\usepackage[noperiod]{jabbrv}
% Use the PLoS provided bibtex style
\bibliographystyle{jneurophys}

@@

>>>>

% Bold the 'Figure #' in the caption and separate it with a period
% Captions will be left justified
\usepackage[labelfont=bf,labelsep=period,justification=raggedright]{caption}
\usepackage[noperiod]{jabbrv}
% Use the PLoS provided bibtex style
\bibliographystyle{plos2009}

@@

If intent could be known during disturbance, we would be able to determine its composition through hypothesis testing. Shadmehr and Mussa-Ivaldi demonstrated that an unchanging intent passed through a simple arm model was sufficient to recreate human-like reaching movements in the presence of force disturbances\cite{shadmehr1994adaptive}. To determine whether or how intent changes following disturbance requires an infinite number of \textit{candidate} intents vying to best reproduce human motion over an infinite number of statistical tests. Optimal feedback control is presently the best and changes intent over the course of a reach\cite{todorov2002optimal}. This approach has many free parameters that need to be tuned to reproduce a reach. By fitting the parameters directly to a library of known intent and state trajectories, a single, maximum-likelihood model could be found. This also represents a means of potentially falsifying optimal feedback control by showing that the maximum likelihood model explains little variance or requires a number of free parameters that grows with the library. Knowing intent would therefore represents a significant advance because it eliminates the need to compare many candidate models.
